Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-16 paper/letter.tex
minor typo

In the multiphase model the best constrained parameters are
the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+12}_{-12}$ \kms,
the clumps outflowing velocity $v_{\infty, \rm{cl}}=55^{+67}_{-37}$
\kms and the fraction of the \lya emission that is  coming
from the cold clumps  
$P_{cl}=0.77^{+0.15}_{-0.44}$. 
The multiphase model assumes that the clouds are distributed over a
sphere of $5$kpc in radius, close to the $\approx 4$kpc physical size
of \tol\ as determined by optical imaging.
The assumed physical size and the velocity dispersion $\sigma_{\rm
  cl}$ correspond to a  dynamical mass of  $M_{\rm
  dyn}=2.9^{+2.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.

>>>>

In the multiphase model the best constrained parameters are
the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+12}_{-12}$ \kms,
the clumps outflowing velocity $v_{\infty, \rm{cl}}=55^{+67}_{-37}$
\kms and the fraction of the \lya emission that is  coming
from the cold clumps  
$P_{cl}=0.77^{+0.15}_{-0.44}$. 
The multiphase model assumes that the clouds are distributed over a
sphere of $5$kpc in radius, close to the $\approx 4$kpc physical size
of \tol\ as determined by optical imaging.
The assumed physical size and the velocity dispersion $\sigma_{\rm
  cl}$ correspond to a  dynamical mass of  $M_{\rm
  dyn}=2.9^{+1.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.
